\bf A Unitary RG-based Auxiliary Model Approach to Strongly-Correlated Electronic Systems

### 2024-04-04 TilingProjectDraft/tilingProject.tex
modularised plotting components

To summarise, the total Hamiltonian we consider is of the form
\begin{equation}\begin{aligned}\label{hamiltonian}
	&-2t\sum_{kx,k y}\left[\cos(ak_x) + \cos(ak_y)\right] c^\dagger_{{\bf k},\sigma}c_{{\bf k},\sigma} + \\
	 &\sum_{{\bf k}_1, {\bf k}_2, \sigma_1, \sigma_2} J_{{\bf k}_1, {\bf k}_2} \vec{S}_d\cdot\frac{1}{2}\vec{\tau}_{\sigma_1,\sigma_2} c^\dagger_{{\bf k}_1,\sigma_1}c_{{\bf k}_2,\sigma_2} -\\
	 &\frac{1}{2}\sum_{1, 2, 3, 4}\sum_\sigma W_{1,2,3,4}~ c^\dagger_{{\bf k}_1,\sigma}c_{{\bf k}_2,\sigma}\left(c^\dagger_{{\bf k}_3,\sigma}c_{{\bf k}_4,\sigma} - c^\dagger_{{\bf k}_3,\bar\sigma}c_{{\bf k}_4,\bar\sigma}\right)~,
\end{aligned}\end{equation}
where \(J_{\left\{ {\bf k}_i \right\} }\) takes one of the two forms in eqs.~\ref{J_dwave} and \ref{J_pwave_nooffsite}, and \(W_{\left\{{\bf k}_i\right\}}\) can similarly take either of the two forms in eqs.~\ref{W_dwave} and \ref{W_pwave_nooffsite}. 
\subsection{Results}
We studied the low-energy physics of this model through a unitary renormalisation group calculation that decouples the high-energy modes of the conduction bath and incorporates their effects in the form of renormalised Hamiltonian couplings. We find that the bath interaction \(W\) remains marginal (does not undergo any renormalisation), while the renormalisation in the momentum-resolved Kondo coupling \(J^{(j)}\) at the \(j^\text{th}\) step is of the form
\begin{equation}\begin{aligned}\label{KondoRGequation}
	\Delta J^{(j)}_{{\bf k}_1, {\bf k}_2} = -\sum_{{\bf q} \in \text{PS}} \frac{J^{(j)}_{{\bf k}_2,{\bf q}} J^{(j)}_{{\bf q},{\bf k}_1} + 4J^{(j)}_{{\bf q}, {\bf \bar q}} W_{{\bf \bar q}, {\bf k}_2, {\bf k}_1, {\bf q}}}{\omega - \frac{1}{2}|\varepsilon_j| + J^{(j)}_{{\bf q}}/4 + W_{{\bf q}}/2}~,
\end{aligned}\end{equation}
where \(\varepsilon_j\) is the energy of the shell being decoupled at the \(j^\text{th}\) step, and the sum is over all momentum states \({\bf q}\) in the particle sector (PS) of the shell \(\varepsilon_j\) (that is, all states that are occupied at \(T=0\) and in the absence of any quantum fluctuations). The Kondo coupling and the RG equation as well have certain symmetries under transformations in the Brillouin zone. If any one of the momenta \({\bf k}_1\) or \({\bf k}_2\) are translated by \(\pi\) (\(k_{1x} \to k_{1x} + \pi, k_{1y} \to k_{1y}+\pi\)), the coupling as well as the RG equation changes sign. Translating both the momenta leads to the reversal of the sign change. 
\begin{equation}\begin{aligned}
	\Delta J^{(j)}_{{\bf k}_1 + \boldsymbol{\pi}, {\bf k}_2} = \Delta J^{(j)}_{{\bf k}_1, {\bf k}_2 + \boldsymbol{\pi}} = -\Delta J^{(j)}_{{\bf k}_1 + \boldsymbol{\pi}, {\bf k}_2 + \boldsymbol{\pi}} = -\Delta J^{(j)}_{{\bf k}_1, {\bf k}_2}~.
\end{aligned}\end{equation}
These transformations involve translating one or both momenta through the center of the Brillouin zone. Further symmetries are obtained by translating both momenta through the \(x-\) or \(y-\)axes:
\begin{equation}\begin{aligned}
	\Delta J^{(j)}_{{\bf k}_1 + \boldsymbol{\pi}, {\bf k}_2} = \Delta J^{(j)}_{{\bf k}_1, {\bf k}_2 + \boldsymbol{\pi}} = -\Delta J^{(j)}_{{\bf k}_1 + \boldsymbol{\pi}, {\bf k}_2 + \boldsymbol{\pi}} = -\Delta J^{(j)}_{{\bf k}_1, {\bf k}_2}~.
\end{aligned}\end{equation}

We now consider some specific cases of these results.

\subsubsection{Same symmetries in the Kondo coupling and bath interaction}
Assuming that both the Kondo interaction and the bath interaction couple to the \(d-\)wave channel, we have the microscopic functional forms 
\begin{equation}\begin{aligned}
	J^{(0)}_{{\bf k},{\bf q}} &= J f_\mathcal{D}({\bf k}) f_\mathcal{D}({\bf q})~,\\
	J^{(0)}_{{\bf \bar q},{\bf q}} &= J f_\mathcal{D}(\pi + {\bf q}) f_\mathcal{D}({\bf q}) = Jf_\mathcal{D}({\bf q})^2 ~,
\end{aligned}\end{equation}
and
\begin{equation}\begin{aligned}
	W_{{\bf \bar q}, {\bf k}_2, {\bf k}_1, {\bf q}} = W f_\mathcal{D}({\bf k}_2)f_\mathcal{D}({\bf k}_1)f_\mathcal{D}({\bf q})^2~,
\end{aligned}\end{equation}
where \(f_\mathcal{D}({\bf k}) = \cos\left( ak_{x} \right) - \cos\left( ak_y \right) \) is the \(d-\)wave symmetric functional form in \(k-\)space
The numerator of the RG equations becomes
\begin{equation}\begin{aligned}
	f_\mathcal{D}({\bf k}_1)f_\mathcal{D}({\bf k}_2)f_\mathcal{D}({\bf q})^4\left[J^2 + 4JW\right] ~.
\end{aligned}\end{equation}
Since a factor of \(f_\mathcal{D}({\bf k}_1)f_\mathcal{D}({\bf k}_2)\) factors out of the RG equation, the Kondo coupling will preserve its momentum dependence during the RG equation, and we can study the RG flow of the amplitude \(J\):
\begin{equation}\begin{aligned}
	\Delta J = \sum_{{\bf q} \in \text{PS}} \frac{-\left(J^2 + 4JW\right) f_\mathcal{D}({\bf q})^4}{\omega - \frac{1}{2}|\varepsilon_j| + \frac{J}{4}f_\mathcal{D}({\bf q})^2 + \frac{W}{2}f_\mathcal{D}({\bf q})^4}~.
\end{aligned}\end{equation}

\subsubsection{Different symmetries in the Kondo coupling and bath interaction}
One can also study the case when the bath interaction has \(p-\)wave symmetry:
\begin{equation}\begin{aligned}
	W_{{\bf \bar q}, {\bf k}_2, {\bf k}_1, {\bf q}} =& \frac{1}{2}W f_\mathcal{P}\left(\pi + {\bf q}, {\bf k}_2, {\bf k}_1, {\bf q}\right) ~,\\
	=& -\frac{1}{2}Wf_\mathcal{P}\left({\bf k}_1, {\bf k}_2\right)~.
\end{aligned}\end{equation}
This choice does not preserve the momentum-dependence of the Kondo coupling, because we can no longer pull out a factor of \(f_\mathcal{D}({\bf k}_1)f_\mathcal{D}({\bf k}_2)\) from the RG equation. At the first step, the RG equation is of the form
\begin{equation}\begin{aligned}
	&\Delta J^{(0)}_{{\bf k}_1, {\bf k}_2} =\\
	&-\sum_{{\bf q} \in \text{PS}} \frac{f_\mathcal{D}({\bf q})^2\left[{J}^2 f_\mathcal{D}({\bf k}_2)f_\mathcal{D}({\bf k}_1) - 2JW f_\mathcal{P}\left({\bf k}_1, {\bf k}_2\right)\right] }{\omega - \frac{1}{2}|\varepsilon_j| + \frac{J}{4}f_\mathcal{D}({\bf q})^2 + \frac{W}{4}}~.
\end{aligned}\end{equation}
The presence of the \(f_\mathcal{P}\) function in the second term leads to a new \(k-\)space dependence of the Kondo coupling at the second step, hence leading to a modified RG equation if one makes the \(k-\)dependence explicit.

>>>>

To summarise, the total Hamiltonian we consider is of the form
\begin{equation}\begin{aligned}\label{hamiltonian}
	&-2t\sum_{kx,k y}\left[\cos(ak_x) + \cos(ak_y)\right] c^\dagger_{{\bf k},\sigma}c_{{\bf k},\sigma} + \\
	 &\sum_{{\bf k}_1, {\bf k}_2, \sigma_1, \sigma_2} J_{{\bf k}_1, {\bf k}_2} \vec{S}_d\cdot\frac{1}{2}\vec{\tau}_{\sigma_1,\sigma_2} c^\dagger_{{\bf k}_1,\sigma_1}c_{{\bf k}_2,\sigma_2} -\\
	 &\frac{1}{2}\sum_{1, 2, 3, 4}\sum_\sigma W_{1,2,3,4}~ c^\dagger_{{\bf k}_1,\sigma}c_{{\bf k}_2,\sigma}\left(c^\dagger_{{\bf k}_3,\sigma}c_{{\bf k}_4,\sigma} - c^\dagger_{{\bf k}_3,\bar\sigma}c_{{\bf k}_4,\bar\sigma}\right)~,
\end{aligned}\end{equation}
where \(J_{\left\{ {\bf k}_i \right\} }\) takes one of the two forms in eqs.~\ref{J_dwave} and \ref{J_pwave_nooffsite}, and \(W_{\left\{{\bf k}_i\right\}}\) can similarly take either of the two forms in eqs.~\ref{W_dwave} and \ref{W_pwave_nooffsite}. 
\subsection{Results}
We studied the low-energy physics of this model through a unitary renormalisation group calculation that decouples the high-energy modes of the conduction bath and incorporates their effects in the form of renormalised Hamiltonian couplings. We find that the bath interaction \(W\) remains marginal (does not undergo any renormalisation), while the renormalisation in the momentum-resolved Kondo coupling \(J^{(j)}\) at the \(j^\text{th}\) step is of the form
\begin{equation}\begin{aligned}\label{KondoRGequation}
	\Delta J^{(j)}_{{\bf k}_1, {\bf k}_2} = -\sum_{{\bf q} \in \text{PS}} \frac{J^{(j)}_{{\bf k}_2,{\bf q}} J^{(j)}_{{\bf q},{\bf k}_1} + 4J^{(j)}_{{\bf q}, {\bf \bar q}} W_{{\bf \bar q}, {\bf k}_2, {\bf k}_1, {\bf q}}}{\omega - \frac{1}{2}|\varepsilon_j| + J^{(j)}_{{\bf q}}/4 + W_{{\bf q}}/2}~,
\end{aligned}\end{equation}
where \(\varepsilon_j\) is the energy of the shell being decoupled at the \(j^\text{th}\) step, and the sum is over all momentum states \({\bf q}\) in the particle sector (PS) of the shell \(\varepsilon_j\) (that is, all states that are occupied at \(T=0\) and in the absence of any quantum fluctuations). The Kondo coupling and the RG equation as well have certain symmetries under transformations in the Brillouin zone. If any one of the momenta \({\bf k}_1\) or \({\bf k}_2\) are translated by \(\pi\) (\(k_{1x} \to k_{1x} + \pi, k_{1y} \to k_{1y}+\pi\)), the coupling as well as the RG equation changes sign. Translating both the momenta leads to the reversal of the sign change. 
\begin{equation}\begin{aligned}
	\Delta J^{(j)}_{{\bf k}_1 + \boldsymbol{\pi}, {\bf k}_2} = \Delta J^{(j)}_{{\bf k}_1, {\bf k}_2 + \boldsymbol{\pi}} = -\Delta J^{(j)}_{{\bf k}_1 + \boldsymbol{\pi}, {\bf k}_2 + \boldsymbol{\pi}} = -\Delta J^{(j)}_{{\bf k}_1, {\bf k}_2}~.
\end{aligned}\end{equation}
These transformations involve translating one or both momenta through the center of the Brillouin zone.

We now consider some specific cases of these results.
\paragraph{Same symmetries in the Kondo coupling and bath interaction}
Assuming that both the Kondo interaction and the bath interaction couple to the \(d-\)wave channel, we have the microscopic functional forms 
\begin{equation}\begin{aligned}
	J^{(0)}_{{\bf k},{\bf q}} &= J f_\mathcal{D}({\bf k}) f_\mathcal{D}({\bf q})~,\\
	J^{(0)}_{{\bf \bar q},{\bf q}} &= J f_\mathcal{D}(\pi + {\bf q}) f_\mathcal{D}({\bf q}) = Jf_\mathcal{D}({\bf q})^2 ~,
\end{aligned}\end{equation}
and
\begin{equation}\begin{aligned}
	W_{{\bf \bar q}, {\bf k}_2, {\bf k}_1, {\bf q}} = W f_\mathcal{D}({\bf k}_2)f_\mathcal{D}({\bf k}_1)f_\mathcal{D}({\bf q})^2~,
\end{aligned}\end{equation}
where \(f_\mathcal{D}({\bf k}) = \cos\left( ak_{x} \right) - \cos\left( ak_y \right) \) is the \(d-\)wave symmetric functional form in \(k-\)space
The numerator of the RG equations becomes
\begin{equation}\begin{aligned}
	f_\mathcal{D}({\bf k}_1)f_\mathcal{D}({\bf k}_2)f_\mathcal{D}({\bf q})^2\left[J^2 + 4JWf_\mathcal{D}({\bf q})^2\right] ~.
\end{aligned}\end{equation}
Since a factor of \(f_\mathcal{D}({\bf k}_1)f_\mathcal{D}({\bf k}_2)\) factors out of the RG equation, the Kondo coupling will preserve its momentum dependence during the RG equation, and we can study the RG flow of the amplitude \(J\):
\begin{equation}\begin{aligned}
	\Delta J = \sum_{{\bf q} \in \text{PS}} \frac{-f_\mathcal{D}({\bf q})^2\left[J^2 + 4JWf_\mathcal{D}({\bf q})^2\right]}{\omega - \frac{1}{2}|\varepsilon_j| + \frac{J}{4}f_\mathcal{D}({\bf q})^2 + \frac{W}{2}f_\mathcal{D}({\bf q})^4}~.
\end{aligned}\end{equation}

\paragraph{Different symmetries in the Kondo coupling and bath interaction}
One can also study the case when the bath interaction has \(p-\)wave symmetry:
\begin{equation}\begin{aligned}
	W_{{\bf \bar q}, {\bf k}_2, {\bf k}_1, {\bf q}} =& \frac{1}{2}W f_\mathcal{P}\left(\pi + {\bf q}, {\bf k}_2, {\bf k}_1, {\bf q}\right) ~,\\
	=& -\frac{1}{2}Wf_\mathcal{P}\left({\bf k}_1, {\bf k}_2\right)~.
\end{aligned}\end{equation}
This choice does not preserve the momentum-dependence of the Kondo coupling, because we can no longer pull out a factor of \(f_\mathcal{D}({\bf k}_1)f_\mathcal{D}({\bf k}_2)\) from the RG equation. At the first step, the RG equation is of the form
\begin{equation}\begin{aligned}
	&\Delta J^{(0)}_{{\bf k}_1, {\bf k}_2} =\\
	&-\sum_{{\bf q} \in \text{PS}} \frac{f_\mathcal{D}({\bf q})^2\left[{J}^2 f_\mathcal{D}({\bf k}_2)f_\mathcal{D}({\bf k}_1) - 2JW f_\mathcal{P}\left({\bf k}_1, {\bf k}_2\right)\right] }{\omega - \frac{1}{2}|\varepsilon_j| + \frac{J}{4}f_\mathcal{D}({\bf q})^2 + \frac{W}{4}}~.
\end{aligned}\end{equation}
The presence of the \(f_\mathcal{P}\) function in the second term leads to a new \(k-\)space dependence of the Kondo coupling at the second step, hence leading to a modified RG equation if one makes the \(k-\)dependence explicit.
